<!-- This script visualises and summarises the RR tables produced by normalization.py-->

```{r}
library(dplyr)
library(ggplot2)
library(stringr)
source("analysis/utils.r")
source("analysis/parse_args.r")

# Set Config
config["test"] <- TRUE
set <- "resp"
REPRESENTATIVE_SEASON <- "Nov-Dec" # Used for percentile chart

```


## Respiratory Measures

The aims of this analysis are to answer the following questions:
1: Which measures show the highest rate ratios?
2: Is there heterogeneity in pressure within winter?
3: Do rate differences show meaningful effect sizes for each measure?
4: Is the pressure metric consistent over time? And by pandemic period?
5: Is pressure increasing in the long-term (i.e. relative to first summer)?
6: Do respiratory metrics capture different pressure signals from each other? Would be indicated by different RR timings.

```{r}

plot_rr_timeseries_by_measure("RR", "season", "prev", "weighted", "resp")
plot_rr_timeseries_by_measure("RD", "season", "prev", "weighted", "resp")
plot_rr_timeseries_by_measure("RR", "season", "first", "weighted", "resp")
plot_rr_timeseries_by_measure("RD", "season", "first", "weighted", "resp")

```

- Do things look different when we look at the average (median) practice rather than the overall national results? I.e. how much of the national signal is driven by a few high-pressure practices?

```{r}
plot_rr_timeseries_by_measure("RR", "season", "prev", "unweighted", "resp")
plot_rr_timeseries_by_measure("RD", "season", "prev", "unweighted", "resp")

# First summer df
plot_rr_timeseries_by_measure("RR", "season", "first", "unweighted", "resp")
plot_rr_timeseries_by_measure("RD", "season", "first", "unweighted", "resp")

```

- How much does the pressure metric vary between practices? I.e. Is pressure similar in the median practice compared to the p75 and p99?

```{r}
plot_rr_timeseries_by_measure("RR", "percentile","prev", "unweighted" ,"resp", REPRESENTATIVE_SEASON)
plot_rr_timeseries_by_measure("RD", "percentile","prev", "unweighted", "resp", REPRESENTATIVE_SEASON)
plot_rr_timeseries_by_measure("RR", "percentile","first", "unweighted", "resp", REPRESENTATIVE_SEASON)
plot_rr_timeseries_by_measure("RD", "percentile","first", "unweighted", "resp", REPRESENTATIVE_SEASON)
```

- How consistent is the pressure effect across practices?

```{r}
plot_rr_timeseries_by_measure("RR", "%_practices","prev", "unweighted","resp", REPRESENTATIVE_SEASON)
plot_rr_timeseries_by_measure("RR", "%_practices","first", "unweighted", "resp", REPRESENTATIVE_SEASON)
```

- How much does the pressure metric vary over time within a practice? 

```{r}
plot_variance_bar_chart("btwn", "resp")
plot_variance_bar_chart("w.in", "resp")
```





## Pathology Test Measures (NEED TO ADD RESULTS FROM CODESPACES TO OUTPUT FOLDER FIRST)

As above

```{r}
pathology_results_df <- read.csv("output/practice_measures_resp/practice_measures_sro_DUMMY/Results_weighted_test.csv")

plot_rr_timeseries_by_measure(pathology_results_df, RR_prev_summr_mp6, "Rate Ratio", season, "Season", "prev summer")
plot_rr_timeseries_by_measure(pathology_results_df, RD_prev_summr_mp6, "Rate Difference", season, "Season", "prev summer")
plot_rr_timeseries_by_measure(pathology_results_df, RR_first_summr_mp6, "Rate Ratio", season, "Season", "first summer")
plot_rr_timeseries_by_measure(pathology_results_df, RD_first_summr_mp6, "Rate Difference", season, "Season", "first summer")
```

- Do things look different when we look at the average (median) practice rather than the overall national results? I.e. how much of the national signal is driven by a few high-pressure practices?

```{r}
pathology_results_df <- read.csv("output/practice_measures_resp/practice_measures_sro_DUMMY/Results_unweighted_yearly_prev_summer_test.csv")

plot_rr_timeseries_by_measure(pathology_results_df, RR_prev_median, "Rate Ratio", season, "Season", "prev summer")
plot_rr_timeseries_by_measure(pathology_results_df, RR_prev_median, "Rate Difference", season, "Season", "prev summer")
plot_rr_timeseries_by_measure(pathology_results_df, RR_first_median, "Rate Ratio", season, "Season", "first summer")
plot_rr_timeseries_by_measure(pathology_results_df, RD_first_median, "Rate Difference", season, "Season", "first summer")

```

- How much does the pressure metric vary between practices? I.e. Is pressure similar in the median practice compared to the p75 and p99?
- How much does the pressure metric vary over time within a practice? 

```{r}
REPRESENTATIVE_SEASON <- "Nov-Dec"

# Pivot percentile columns to long format so that they can be set as colour
pathology_results_df <- read.csv("output/practice_measures_resp/practice_measures_sro_DUMMY/Results_unweighted_yearly_prev_summer_test.csv")

pathology_results_long <- pathology_results_df %>%
    pivot_longer(cols = c(RR_prev_summr_p01, RR_prev_summr_p25, RR_prev_median, RR_prev_summr_p75, RR_prev_summr_p99), names_to = "percentile", values_to = "RR_prev_summer")

filter(pathology_results_long, season == REPRESENTATIVE_SEASON) %>%
    plot_rr_timeseries_by_measure(RR_prev_summer, "Rate Ratio", percentile, "Percentile", "first summer")

```



