<!-- This script visualises and summarises the RR tables produced by normalization.py-->

```{r}
library(dplyr)
library(ggplot2)
library(stringr)
source("analysis/utils.r")
source("analysis/parse_args.r")

# Set Config
config["test"] <- TRUE
```


## Respiratory Measures

The aims of this analysis are to answer the following questions:
1: Which measures show the highest rate ratios?
2: Is there heterogeneity in pressure within winter?
3: Do rate differences show meaningful effect sizes for each measure?
4: Is the pressure metric consistent over time? And by pandemic period?
5: Is pressure increasing in the long-term (i.e. relative to first summer)?
6: Do respiratory metrics capture different pressure signals from each other? Would be indicated by different RR timings.

```{r}
resp_results_df <- read.csv("output/practice_measures_resp/practice_measures_resp_DUMMY/Results_weighted_test.csv")

rr_timeseries_by_measure <- function(df, y_var, y_label, colour_var, colour_label, baseline){
    "
    This function produces a line plot, coloured by season, faceted by measure
    Args:
        df: dataframe containing the results of the rate ratio     calculations
        y_var: the variable to plot on the y-axis (e.g. RR_prev_summr_mp6)
        colour_var: the variable to colour the lines by (e.g. season)
        y_label: the label for the y-axis
        colour_label: the label for the colour legend
        baseline: the baseline category for comparison
    "
    if (colour_label == "Season") {
        linetype_mapping <- c(
            "Sep-Oct" = "dashed",
            "Nov-Dec" = "solid",
            "Jan-Feb" = "solid",
            "Mar-Apr" = "dashed"
        )
    }
    else if(colour_label == "Percentile") {
        linetype_mapping <- c(
            "RR_prev_summr_p01" = "dotted",
            "RR_prev_summr_p25" = "dashed",
            "RR_prev_median" = "solid",
            "RR_prev_summr_p75" = "dashed",
            "RR_prev_summr_p99" = "dotted"
        )
    }

    line_plot <- df %>%
        ggplot(aes(x = summer_year, y = {{ y_var }}, color = {{ colour_var }}, linetype = {{ colour_var }})) +
        geom_line() +
        geom_point() +
        scale_linetype_manual(values = linetype_mapping) +
        labs(title = glue("{y_label} (vs {baseline}) Over Time by {colour_label}"),
            x = "year",
            y = y_label) +
        theme_minimal() +
        facet_grid(rows = vars(measure)) +
        theme(legend.title = element_blank())

    return(line_plot)
}

rr_timeseries_by_measure(resp_results_df, RR_prev_summr_mp6, "Rate Ratio", season, "Season", "prev summer")
rr_timeseries_by_measure(resp_results_df, RD_prev_summr_mp6, "Rate Difference", season, "Season", "prev summer")
rr_timeseries_by_measure(resp_results_df, RR_first_summr_mp6, "Rate Ratio", season, "Season", "first summer")
rr_timeseries_by_measure(resp_results_df, RD_first_summr_mp6, "Rate Difference", season, "Season", "first summer")

```

- Do things look different when we look at the average (median) practice rather than the overall national results? I.e. how much of the national signal is driven by a few high-pressure practices?

```{r}
resp_results_df <- read.csv("output/practice_measures_resp/practice_measures_resp_DUMMY/Results_unweighted_yearly_prev_summer_test.csv")

rr_timeseries_by_measure(resp_results_df, RR_prev_median, "Rate Ratio", season, "Season", "prev summer")
rr_timeseries_by_measure(resp_results_df, RR_prev_median, "Rate Difference", season, "Season", "prev summer")
rr_timeseries_by_measure(resp_results_df, RR_first_median, "Rate Ratio", season, "Season", "first summer")
rr_timeseries_by_measure(resp_results_df, RD_first_median, "Rate Difference", season, "Season", "first summer")

```

- How much does the pressure metric vary between practices? I.e. Is pressure similar in the median practice compared to the p75 and p99?
- How much does the pressure metric vary over time within a practice? 

```{r}
REPRESENTATIVE_SEASON <- "Nov-Dec"

# Pivot percentile columns to long format so that they can be set as colour
resp_results_df <- read.csv("output/practice_measures_resp/practice_measures_resp_DUMMY/Results_unweighted_yearly_prev_summer_test.csv")

resp_results_long <- resp_results_df %>%
    pivot_longer(cols = c(RR_prev_summr_p01, RR_prev_summr_p25, RR_prev_median, RR_prev_summr_p75, RR_prev_summr_p99), names_to = "percentile", values_to = "RR_prev_summer")

filter(resp_results_long, season == REPRESENTATIVE_SEASON) %>%
    rr_timeseries_by_measure(RR_prev_summer, "Rate Ratio", percentile, "Percentile", "first summer")

```


## Pathology Test Measures (NEED TO ADD RESULTS FROM CODESPACES TO OUTPUT FOLDER FIRST)

As above

```{r}
pathology_results_df <- read.csv("output/practice_measures_resp/practice_measures_sro_DUMMY/Results_weighted_test.csv")

rr_timeseries_by_measure(pathology_results_df, RR_prev_summr_mp6, "Rate Ratio", season, "Season", "prev summer")
rr_timeseries_by_measure(pathology_results_df, RD_prev_summr_mp6, "Rate Difference", season, "Season", "prev summer")
rr_timeseries_by_measure(pathology_results_df, RR_first_summr_mp6, "Rate Ratio", season, "Season", "first summer")
rr_timeseries_by_measure(pathology_results_df, RD_first_summr_mp6, "Rate Difference", season, "Season", "first summer")
```





