<!-- This script visualises and summarises the RR tables produced by normalization.py-->

```{r}
library(here)
# Now paths like "analysis/utils.r" work relative to project root
library(dplyr)
library(ggplot2)
library(stringr)
source(here("analysis/utils.r"))
source(here("analysis/parse_args.r"))

# Set Config
config["test"] <- TRUE
set <- "resp"
REPRESENTATIVE_SEASON <- "Nov-Dec" # Used for percentile chart

```

## Respiratory Measures

The aims of this analysis are to answer the following questions:
1: Which measures show the highest rate ratios?
2: Is there heterogeneity in pressure within winter?
3: Do rate differences show meaningful effect sizes for each measure?
4: Is the pressure metric consistent over time? And by pandemic period?
5: Is pressure increasing in the long-term (i.e. relative to first summer)?
6: Do respiratory metrics capture different pressure signals from each other? Would be indicated by different RR timings.

```{r}
source("analysis/utils.r")
plot_rr_timeseries_by_measure("RR", "season", "prev", "weighted", "resp", "sensitive")
plot_rr_timeseries_by_measure("RD", "season", "prev", "weighted", "resp", "sensitive")
plot_rr_timeseries_by_measure("RR", "season", "prev", "weighted", "resp", "specific")
plot_rr_timeseries_by_measure("RD", "season", "prev", "weighted", "resp", "specific")
```
```{r}
plot_rr_timeseries_by_measure("RR", "season", "first", "weighted", "resp", "specific")
plot_rr_timeseries_by_measure("RR", "season", "first", "weighted", "resp", "sensitive")
plot_rr_timeseries_by_measure("RD", "season", "first", "weighted", "resp", "sensitive")
plot_rr_timeseries_by_measure("RD", "season", "first", "weighted", "resp", "specific")

```

- Do things look different when we look at the average (median) practice rather than the overall national results? I.e. how much of the national signal is driven by a few high-pressure practices?

```{r}
source("analysis/utils.r")

plot_rr_timeseries_by_measure("RR", "season", "prev", "unweighted", "resp", "sensitive")
plot_rr_timeseries_by_measure("RD", "season", "prev", "unweighted", "resp", "sensitive")
plot_rr_timeseries_by_measure("RR", "season", "prev", "unweighted", "resp", "specific")
plot_rr_timeseries_by_measure("RD", "season", "prev", "unweighted", "resp", "specific")
```
```{r}
# First summer df
plot_rr_timeseries_by_measure("RR", "season", "first", "unweighted", "resp", "sensitive")
plot_rr_timeseries_by_measure("RD", "season", "first", "unweighted", "resp", "sensitive")

```

- How much does the pressure metric vary between practices? I.e. Is pressure similar in the median practice compared to the p75 and p99?

```{r}
source("analysis/utils.r")

plot_rr_timeseries_by_measure("RR", "percentile","prev", "unweighted" ,"resp",  "sensitive", REPRESENTATIVE_SEASON)
plot_rr_timeseries_by_measure("RD", "percentile","prev", "unweighted", "resp",  "sensitive", REPRESENTATIVE_SEASON)
plot_rr_timeseries_by_measure("RR", "percentile","prev", "unweighted" ,"resp",  "specific", REPRESENTATIVE_SEASON)
plot_rr_timeseries_by_measure("RD", "percentile","prev", "unweighted", "resp", "specific", REPRESENTATIVE_SEASON)
```
```{r}
plot_rr_timeseries_by_measure("RR", "percentile","f irst", "unweighted" ,"resp",  "sensitive", REPRESENTATIVE_SEASON,)
plot_rr_timeseries_by_measure("RD", "percentile","first", "unweighted", "resp",  "sensitive", REPRESENTATIVE_SEASON,)
plot_rr_timeseries_by_measure("RR", "percentile","first", "unweighted" ,"resp",  "specific", REPRESENTATIVE_SEASON)
plot_rr_timeseries_by_measure("RD", "percentile","first", "unweighted", "resp", "specific", REPRESENTATIVE_SEASON)
```

- How consistent is the pressure effect across practices?

```{r}
source("analysis/utils.r")

plot_rr_timeseries_by_measure("RR", "%_practices","prev", "unweighted","resp",   subset = "specific")

plot_rr_timeseries_by_measure("RR", "%_practices","prev", "unweighted","resp", subset = "sensitive")

```
```{r}
plot_rr_timeseries_by_measure("RR", "%_practices","first", "unweighted", "resp", REPRESENTATIVE_SEASON)
```

- How much does the pressure metric vary over time within a practice? 

```{r}
source("analysis/utils.r")

plot_variance_bar_chart("btwn", "resp")
plot_variance_bar_chart("w.in", "resp")
```





# Pathology Test Measures (NEED TO ADD RESULTS FROM CODESPACES TO OUTPUT FOLDER FIRST)

## Respiratory Measures

The aims of this analysis are to answer the following questions:
1: Which measures show the highest rate ratios?
2: Is there heterogeneity in pressure within winter?
3: Do rate differences show meaningful effect sizes for each measure?
4: Is the pressure metric consistent over time? And by pandemic period?
5: Is pressure increasing in the long-term (i.e. relative to first summer)?
6: Do respiratory metrics capture different pressure signals from each other? Would be indicated by different RR timings.

```{r}
source("analysis/utils.r")

plot_rr_timeseries_by_measure("RR", "season", "prev", "weighted", "sro", "tests")
plot_rr_timeseries_by_measure("RD", "season", "prev", "weighted", "sro", "tests")
plot_rr_timeseries_by_measure("RR", "season", "prev", "weighted", "sro", "other")
plot_rr_timeseries_by_measure("RD", "season", "prev", "weighted", "sro", "other")
```
```{r}
plot_rr_timeseries_by_measure("RR", "season", "first", "weighted", "sro", "tests")
plot_rr_timeseries_by_measure("RD", "season", "first", "weighted", "sro", "tests")

```

- Do things look different when we look at the average (median) practice rather than the overall national results? I.e. how much of the national signal is driven by a few high-pressure practices?

```{r}
source("analysis/utils.r")

plot_rr_timeseries_by_measure("RR", "season", "prev", "unweighted", "sro", "tests")
plot_rr_timeseries_by_measure("RD", "season", "prev", "unweighted", "sro", "tests")
plot_rr_timeseries_by_measure("RR", "season", "prev", "unweighted", "sro", "other")
plot_rr_timeseries_by_measure("RD", "season", "prev", "unweighted", "sro", "other")
```
```{r}
# First summer df
plot_rr_timeseries_by_measure("RR", "season", "first", "unweighted", "sro", "tests")
plot_rr_timeseries_by_measure("RD", "season", "first", "unweighted", "sro", "tests")

```

- How much does the pressure metric vary between practices? I.e. Is pressure similar in the median practice compared to the p75 and p99?

```{r}
source("analysis/utils.r")

plot_rr_timeseries_by_measure("RR", "percentile","prev", "unweighted" ,"sro",  "sensitive", REPRESENTATIVE_SEASON)
plot_rr_timeseries_by_measure("RD", "percentile","prev", "unweighted", "sro",  "sensitive", REPRESENTATIVE_SEASON)
plot_rr_timeseries_by_measure("RR", "percentile","prev", "unweighted" ,"sro",  "specific", REPRESENTATIVE_SEASON)
plot_rr_timeseries_by_measure("RD", "percentile","prev", "unweighted", "sro", "specific", REPRESENTATIVE_SEASON)
```
```{r}
plot_rr_timeseries_by_measure("RR", "percentile","f irst", "unweighted" ,"sro",  "sensitive", REPRESENTATIVE_SEASON,)
plot_rr_timeseries_by_measure("RD", "percentile","first", "unweighted", "sro",  "sensitive", REPRESENTATIVE_SEASON,)
plot_rr_timeseries_by_measure("RR", "percentile","first", "unweighted" ,"sro",  "specific", REPRESENTATIVE_SEASON)
plot_rr_timeseries_by_measure("RD", "percentile","first", "unweighted", "sro", "specific", REPRESENTATIVE_SEASON)
```

- How consistent is the pressure effect across practices?

```{r}
source("analysis/utils.r")

plot_rr_timeseries_by_measure("RR", "%_practices","prev", "unweighted","sro",   subset = "tests", representative_season = REPRESENTATIVE_SEASON)

plot_rr_timeseries_by_measure("RR", "%_practices","prev", "unweighted","sro", subset = "other", representative_season = REPRESENTATIVE_SEASON)
```

- How much does the pressure metric vary over time within a practice? 

```{r}
source("analysis/utils.r")

plot_variance_bar_chart("btwn", "sro")
plot_variance_bar_chart("w.in", "sro")
