<!-- This script visualises and summarises the RR tables produced by normalization.py-->

```{r}
library(dplyr)
library(ggplot2)
library(stringr)
source("analysis/utils.r")
source("analysis/parse_args.r")

# Set Config
config["test"] <- TRUE
set <- "resp"
```


## Respiratory Measures

The aims of this analysis are to answer the following questions:
1: Which measures show the highest rate ratios?
2: Is there heterogeneity in pressure within winter?
3: Do rate differences show meaningful effect sizes for each measure?
4: Is the pressure metric consistent over time? And by pandemic period?
5: Is pressure increasing in the long-term (i.e. relative to first summer)?
6: Do respiratory metrics capture different pressure signals from each other? Would be indicated by different RR timings.

```{r}

plot_rr_timeseries_by_measure <- function(y_var, colour_var, baseline, weighting, set){
    "
    This function produces a line plot, coloured by season, faceted by measure
    Args:
        df: dataframe containing the results of the rate ratio calculations
        y_var: string name of the variable to plot on the y-axis (e.g. 'RR_prev_summr_mp6')
        colour_var: string name of the variable to colour the lines by (e.g. 'season')
        colour_label: the label for the colour legend
        baseline: the baseline category for comparison
    "

    if (colour_var == "season") {
        linetype_mapping <- c(
            "Sep-Oct" = "dashed",
            "Nov-Dec" = "solid",
            "Jan-Feb" = "solid",
            "Mar-Apr" = "dashed"
        )
        colour_mapping <- c(
            "Sep-Oct" = "#1b9e77",
            "Nov-Dec" = "#d95f02",
            "Jan-Feb" = "#7570b3",
            "Mar-Apr" = "#e7298a"
        )
    }
    else if(colour_var == "percentile") {
        linetype_mapping <- c(
            "dotted",
            "dashed",
            "solid",
            "dashed",
            "dotted"
        )
        names(linetype_mapping) <- c(
            glue("{y_var}_{baseline}_summr_p01"),
            glue("{y_var}_{baseline}_summr_p25"),
            glue("{y_var}_{baseline}_median"),
            glue("{y_var}_{baseline}_summr_p75"),
            glue("{y_var}_{baseline}_summr_p99")
        )
        colour_mapping <- c(
            "#0011ff",
            "#0011ff",
            "#0011ff",
            "#0011ff",
            "#0011ff"
        )
        names(colour_mapping) <- names(linetype_mapping)
    }
    if (weighting == "weighted") {
        df_name <- paste(glue("weighted"))
        y_col <- paste(glue("{y_var}_{baseline}_summr_mp6"))
    }
    else if ((weighting == "unweighted") & (colour_var == "season")) {
        df_name <- paste(glue("unweighted_yearly_{baseline}_summer"))
        y_col <- paste(glue("{y_var}_{baseline}_median"))
    }
    else if ((weighting == "unweighted") & (colour_var == "percentile")) {
        df_name <- paste(glue("unweighted_yearly_{baseline}_summer"))
        y_col <- paste(glue("{y_var}_{baseline}_summer"))
    }

    # Load weighted results
    results_df <- read.csv(glue("output/practice_measures_{set}/practice_measures_{set}_DUMMY/Results_{df_name}_test.csv"))

    line_plot <- results_df |>
        ggplot(aes(x = summer_year, y = .data[[y_col]], color = .data[[colour_var]], linetype = .data[[colour_var]])) +
        geom_line() +
        geom_point() +
        scale_linetype_manual(values = linetype_mapping) +
        scale_color_manual(values = colour_mapping) +
        labs(title = glue("{y_var} (vs {baseline} summer) Over Time by {colour_var}"),
            x = "year",
            y = y_var) +
        theme_minimal() +
        facet_grid(rows = vars(measure)) +
        theme(legend.title = element_blank())

    return(line_plot)
}

plot_rr_timeseries_by_measure("RR", "season", "prev", "weighted", "resp")
plot_rr_timeseries_by_measure("RD", "season", "prev", "weighted", "resp")
plot_rr_timeseries_by_measure("RR", "season", "first", "weighted", "resp")
plot_rr_timeseries_by_measure("RD", "season", "first", "weighted", "resp")

```

- Do things look different when we look at the average (median) practice rather than the overall national results? I.e. how much of the national signal is driven by a few high-pressure practices?

```{r}
plot_rr_timeseries_by_measure("RR", "season", "prev", "unweighted", "resp")
plot_rr_timeseries_by_measure("RD", "season", "prev", "unweighted", "resp")

# First summer df
plot_rr_timeseries_by_measure("RR", "season", "first", "unweighted", "resp")
plot_rr_timeseries_by_measure("RD", "season", "first", "unweighted", "resp")

```

- How much does the pressure metric vary between practices? I.e. Is pressure similar in the median practice compared to the p75 and p99?

```{r}
REPRESENTATIVE_SEASON <- "Nov-Dec" # Used for percentile chart

plot_percentile_timeseries <- function(y_var, baseline, set){
    "This function produces a plot of percentiles
    Args:
        y_var: string name of the variable to plot on the y-axis (e.g. 'RR')
        baseline: the baseline category for comparison (e.g. 'prev' or 'first')
        set: Set of measures (e.g. 'resp' or 'sro')"
    
    # Load first or previous summer baseline df
    resp_results_df <- read.csv(glue("output/practice_measures_{set}/practice_measures_{set}_DUMMY/Results_unweighted_yearly_{baseline}_summer_test.csv"))

    # Pivot percentile columns to long format so that they can be set as colour
    results_long <- results_df %>%
        pivot_longer(cols = c(glue("{y_var}_{baseline}_summr_p01"), glue("{y_var}_{baseline}_summr_p25"), glue("{y_var}_{baseline}_median"), glue("{y_var}_{baseline}_summr_p75"), glue("{y_var}_{baseline}_summr_p99")), names_to = "percentile", values_to = as.character(glue("{y_var}_{baseline}_summer")))
    
    # Percentile chart - do we need RD as well?
    filter(results_long, season == REPRESENTATIVE_SEASON) %>%
        plot_rr_timeseries_by_measure(y_var, "percentile", baseline, "unweighted", set)
}

plot_percentile_timeseries("RR", "prev", "resp")
plot_percentile_timeseries("RD", "prev", "resp")
plot_percentile_timeseries("RR", "first", "resp")
plot_percentile_timeseries("RD", "first", "resp")
```

- How much does the pressure metric vary over time within a practice? 

```{r}

plot_variance_bar_chart <- function(df, var_type, set){
    "This function produces a bar chart of the variance of the pressure metric
    Args:
        df: dataframe containing the results of the variance calculations
        var_type: string name of the type of variance to plot (e.g. 'btwn' or 'w.in')
        set: Set of measures (resp or sro)"
    
    # Load variance df
    variance_df <- read.csv(glue("output/practice_measures_{set}/practice_measures_{set}_DUMMY/Results_variances_test.csv"))

    variance_plot <- df %>%
        ggplot(aes(x = measure, y = .data[[glue("var_rate_{var_type}_prac_season_median")]], fill = season)) +
        geom_col(position = position_dodge(width = 0.9)) +
        labs(title = glue("Variance in rate {var_type} practices inby Season"),
            x = "Season",
            y = glue("Variance in rate {var_type} practices")) +
        theme_minimal() +
        theme(legend.title = element_blank())
    
    return(variance_plot)
}

plot_variance_bar_chart(variance_df, "btwn", "prev", "resp")
plot_variance_bar_chart(variance_df, "w.in", "first", "resp")
```





## Pathology Test Measures (NEED TO ADD RESULTS FROM CODESPACES TO OUTPUT FOLDER FIRST)

As above

```{r}
pathology_results_df <- read.csv("output/practice_measures_resp/practice_measures_sro_DUMMY/Results_weighted_test.csv")

plot_rr_timeseries_by_measure(pathology_results_df, RR_prev_summr_mp6, "Rate Ratio", season, "Season", "prev summer")
plot_rr_timeseries_by_measure(pathology_results_df, RD_prev_summr_mp6, "Rate Difference", season, "Season", "prev summer")
plot_rr_timeseries_by_measure(pathology_results_df, RR_first_summr_mp6, "Rate Ratio", season, "Season", "first summer")
plot_rr_timeseries_by_measure(pathology_results_df, RD_first_summr_mp6, "Rate Difference", season, "Season", "first summer")
```

- Do things look different when we look at the average (median) practice rather than the overall national results? I.e. how much of the national signal is driven by a few high-pressure practices?

```{r}
pathology_results_df <- read.csv("output/practice_measures_resp/practice_measures_sro_DUMMY/Results_unweighted_yearly_prev_summer_test.csv")

plot_rr_timeseries_by_measure(pathology_results_df, RR_prev_median, "Rate Ratio", season, "Season", "prev summer")
plot_rr_timeseries_by_measure(pathology_results_df, RR_prev_median, "Rate Difference", season, "Season", "prev summer")
plot_rr_timeseries_by_measure(pathology_results_df, RR_first_median, "Rate Ratio", season, "Season", "first summer")
plot_rr_timeseries_by_measure(pathology_results_df, RD_first_median, "Rate Difference", season, "Season", "first summer")

```

- How much does the pressure metric vary between practices? I.e. Is pressure similar in the median practice compared to the p75 and p99?
- How much does the pressure metric vary over time within a practice? 

```{r}
REPRESENTATIVE_SEASON <- "Nov-Dec"

# Pivot percentile columns to long format so that they can be set as colour
pathology_results_df <- read.csv("output/practice_measures_resp/practice_measures_sro_DUMMY/Results_unweighted_yearly_prev_summer_test.csv")

pathology_results_long <- pathology_results_df %>%
    pivot_longer(cols = c(RR_prev_summr_p01, RR_prev_summr_p25, RR_prev_median, RR_prev_summr_p75, RR_prev_summr_p99), names_to = "percentile", values_to = "RR_prev_summer")

filter(pathology_results_long, season == REPRESENTATIVE_SEASON) %>%
    plot_rr_timeseries_by_measure(RR_prev_summer, "Rate Ratio", percentile, "Percentile", "first summer")

```



